Contextual recruitment of selective attention can be updated via changes in task-relevance

### 2018-12-10 manuscript.Rmd
first draft
update / clean up

The importance of the latter issue becomes increasingly clear if we speculate about context-specificity in more complex, real-world environments. Consider myself, right now, writing this article in a coffee shop. The coffee shop is a complex environment that contains a multitude of contextual cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which I have had many different experiences applying attentional control. Although my laptop might cue attentional processing helpful for finishing this article, other features of the coffee shop might cue other, unhelpful attentional processing related to other experiences like socializing and people-watching. This is all to say that our environments, and experiences within them, afford many different associative relationships between cognitive processing and environmental cues. What then determines which associative relationships will be used to guide attention (or even if such associative relationships are used at all)?

@@

```{r analysis}
source("data-analysis/analysis.R")
```

@@

![ ](images/table1.pdf) 
\endgroup

>>>>

The importance of the latter issue may become clearer if we speculate about context-specificity in more complex, real-world environments. Consider myself, right now, writing this article in a coffee shop. The coffee shop is a complex environment that contains a multitude of contextual cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which I have had many different experiences applying attentional control. Although my laptop might cue attentional processing helpful for finishing this article, other features of the coffee shop might cue other, unhelpful attentional processing related to other experiences like socializing and people-watching. This is all to say that our environments, and experiences within them, afford many different associative relationships between cognitive processing and environmental cues. What then determines which associative relationships will be used to guide attention (or even if such associative relationships are used at all)?

@@

```{r analysis, echo=FALSE, include=FALSE, eval=TRUE}
source("data-analysis/analysis.R")
```

@@

![ ](images/table1.png) 
\endgroup
